---
title: "Codebook"
format: 
  html:
    code-fold: true
    code-copy: true
    code-tools: true
    embed-resources: true
    df-print: kable
    toc: true
    toc-location: right
    fig-format: svg
    page-layout: full
    fig-height: 4
    fig-width:  9
    fig-align: center
execute:
  warning: false
  messages: false
editor_options: 
  chunk_output_type: console
---

```{r packages}
#| code-summary: "Load packages"

library(tidyverse)
library(kableExtra)
```


This page contains the **codebooks** (i.e., description of each variable) for the data files `data_raw_estimation_*.csv`, `data_tidy_combined.csv` and `data_analysis_*.csv`. The corresponding data files can be downloaded from the [Github](https://github.com/dizyd/Estimation-processes-in-real-world-domains/tree/main/Data). 

```{r function}
#| code-summary: "Helper function"

# The make_df_readme function generates a summary of a given data frame in R, creating a descriptive table that outlines the structure and content of the data frame. If the add_examples parameter is set to TRUE (the default), the function samples two random rows from df as examples.

make_df_readme <- function(df, desc, add_examples = TRUE, digits = 2, n_examples = 4) {
  
  # Input validation
  if (!is.data.frame(df)) stop("The input 'df' must be a data frame.")
  if (!is.character(desc) || length(desc) != ncol(df)) 
    stop("The 'desc' argument must be a character vector with the same length as the number of columns in 'df'.")
  if (!is.numeric(digits) || digits < 0) stop("The 'digits' argument must be a non-negative integer.")
  if (!is.numeric(n_examples) || n_examples <= 0) stop("The 'n_examples' argument must be a positive integer.")
  
  # Create the initial summary dataframe
  temp0 <- data.frame(
    "Variable"       = names(df),
    "Type"           = sapply(df, function(x) class(x)[1]), # Ensure it handles multiple class objects correctly
    "Description"    = desc,
    stringsAsFactors = FALSE
  )
  
  row.names(temp0) <- NULL
  
  # Optionally add examples
  if (add_examples) {
    sampled_rows   <- df[sample(1:nrow(df), n_examples), ]
    example_values <- apply(sampled_rows, 2, function(col) {
      if (is.numeric(col)) {
        col <- printnum(col, digits=digits)
      }
      paste(col, collapse = ", ")
    })
    
    temp0$`Example values` <- example_values
  }
  
  return(temp0)
}
```


# `data_raw_estimation_*.csv`


```{r items1}
#| code-summary: "Read in data"

# read in data
df_food <- read_csv2("data_raw_estimation_food.csv")
```

The files `data_raw_estimation_*.csv` contain the raw data from the estimation experiment, separated by domain (food, mammals, countries). Each dataset includes the following variables:
                       
```{r}

desc <- c("Unique person identifier",
          "Date of participationd",
          "Phase of the experiment [training, testing]",
          "Number of trainings block [1-10]",
          "Number of trial in the corresponding phase and block",
          "Item label",
          "Image file name of the corresponding item",
          "Was this item in the training phase? [1 = yes, 0 = no]",
          "Estimated criterion of this item by the participant",
          "True criterion value of the item",
          "Overall response time in ms for each estimate (from stimulus shown until confirmed button clicked)",
          "Experimental: Time in ms the confirm-button was clicked (i.e., mouse-down) on each trial",
          "Internal experimental clock time when the stimulus was shown",
          "Internal experimental clock time when the first input was made by the participant",
          "Individual keys pressed by the participants to type in their judgment (NA -> back/delete button)",
          "Internal experimental clock time for all inputs",
          "Controle question: ~ How did you make your estimates ? Did you use a specific strategy?",
          "Self-reported knowledge of food/mammals/countries [1-7]",
          "Controle question: ~ Should your date be used for analyis? [yes, no]",
          "Controle question: ~ Did you use any form of aid? [yes, no]",
          "Age of the participant",
          "Gender of the participant [female, male, non_binary]",
          "Controle question: ~ Were you able to work on the study undisturbed? [yes, no]",
          "Controle question: ~ What disturbtions have occurred?",
          "Controle question: ~ Where there any technical problems [yes, no]",
          "Controle question: ~ Describe the problem") 
  

tbl <- make_df_readme(df_food,desc)

if (knitr::is_latex_output()) {
   tbl %>%
      kable(format="latex", booktabs = TRUE)   %>% 
      kableExtra::kable_styling(tbl, latex_options = 'scale_down')
} else {
  tbl %>% 
    kable(format     = "html",
          table.attr = 'class="table table-striped table-hover"',
          escape     = FALSE) %>%
    kable_styling(fixed_thead = T)
}

```

# `data_tidy_combined.csv`

```{r items2}
#| code-summary: "Read in data"

# read in data
df_tidy <- read_csv("data_tidy_combined.csv")
```

The file `data_tidy_combined.csv` contains the tidy data (i.e., after filtering of participants) together for all domains. It has `r nrow(df_tidy)` rows and has the same variables as the `data_raw_estimation_*.csv` datasets with the additional variable `domain` which indicates the domain (Food, Mammals, Countries) the corresponding participant was in.


# `data_analysis_*.csv`


```{r items3}
#| code-summary: "Read in data"

# read in data
df_temp <- read_csv("data_analysis_food.csv")
```

The files `data_analysis_*.csv` are in the long format and contain information about each participants estimates in the testing phase. The general variables are: 
                       
```{r}

desc <- c("Numeric item identifier",
          "Item label",
          "Image file name of the corresponding item",
          "Was this item in the training phase? [1 = yes, 0 = no]",
          "True criterion value of the item") 
  

tbl <- make_df_readme(df_temp[,c(1:5)],desc)

if (knitr::is_latex_output()) {
   tbl %>%
      kable(format="latex", booktabs = TRUE)   %>% 
      kableExtra::kable_styling(tbl, latex_options = 'scale_down')
} else {
  tbl %>% 
    kable(format     = "html",
          table.attr = 'class="table table-striped table-hover"',
          escape     = FALSE) %>%
    kable_styling(fixed_thead = T)
}

```

The remaining variables/columns are named after each participants `ID` (i.e., unique person identifier as present in `data_tidy_combined.csv` or the `data_raw_estimation_*.csv`) and contain the estimated criterion value of this participant for the correpsonding item.